A Domain-Driven, Generative Data Model for BigPetStore

### 2014-10-12 bdcloud_paper/latex/paper.tex
delete deade code
Fix typos found by reviewers

%Both developers and users of big data systems benefit from realistic example applications.  For developers, such applications are useful for testing, benchmarking, and evaluating design choices; for users, example applications provide starting points for learning methods, developing their own applications, and implementing new analytics workflows.

@@

\section{Introduction}
Big data applications process large, dynamics, multidimensional data sets with the general goal of information and knowledge extraction.  With the wide variety of big data tools available and lagging documentation, both developers and users of big data systems benefit from the availability of realistic example applications.  For developers, such applications are useful for testing, benchmarking, and evaluating design choices; for users, example applications provide starting points for learning methods, developing their own applications, and implementing new analytics workflows.

@@

Until such purely generic methods reach maturity, BigPetStore's needs are best met by a customized, domain-driven model. Another example of such a model is The Information Discovery and Analysis System (IDAS) Data Set Generator (IDSG) \cite{Jeske2005,Lin2006}. IDSG was developed to to test the effectiveness of IDASs in identifying potential terrorism threat scenarios using synthetic data.  Like BigPetStore, the developers of IDSG needed to avoid licensing restrictions and privacy issues associated with real data.

>>>>

@@

\section{Introduction}
Big data applications process large, dynamic, multidimensional data sets with the general goal of information and knowledge extraction.  With the wide variety of big data tools available and lagging documentation, both developers and users of big data systems benefit from the availability of realistic example applications.  For developers, such applications are useful for testing, benchmarking, and evaluating design choices; for users, example applications provide starting points for learning methods, developing their own applications, and implementing new analytics workflows.

@@

Until such purely generic methods reach maturity, BigPetStore's needs are best met by a customized, domain-driven model. Another example of such a model is The Information Discovery and Analysis System (IDAS) Data Set Generator (IDSG) \cite{Jeske2005,Lin2006}. IDSG was developed to test the effectiveness of IDASs in identifying potential terrorism threat scenarios using synthetic data.  Like BigPetStore, the developers of IDSG needed to avoid licensing restrictions and privacy issues associated with real data.
